Dataset Summary

### 2018-07-06 Overview.Rmd
Add distributions of ages and plots of age vs weight

```{r setup, include=FALSE, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
library(readr)
library(dplyr)
library(skimr)
library(ggplot2)
library(scales)
```

@@

The data is big, but not so large that we can't use our standard tools on a desktop. I'd suggest using packages from the [tidyverse](https://www.tidyverse.org/) family, in particular `readr`, `dplyr`, `ggplot2`, `skimr`, `scales`.

@@

# make a plot
tibble(percent_NA = NA_count) %>% 
  ggplot(aes(percent_NA)) + geom_histogram()
```

@@

Weights by center:
```{r}
ggplot(data, aes(x=weight)) + 
  geom_histogram() + 
  facet_wrap( ~ production_center, ncol=1)
```

@@

## Procedure

@@

Next want to visualise the above, but so far the plot is unmanagable (need to improve):

>>>>

```{r setup, include=FALSE, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
library(readr)
library(dplyr)
library(skimr)
library(ggplot2)
library(scales)
library(viridis)
```

@@

The data is big, but not so large that we can't use our standard tools on a desktop. I'd suggest using packages from the [tidyverse](https://www.tidyverse.org/) family, in particular `readr`, `dplyr`, `ggplot2`, `skimr`, `scales`, `viridis`.

@@

# make a plot
tibble(percent_NA = NA_count) %>% 
  ggplot(aes(percent_NA)) + geom_histogram(bins=50)
```

@@

Weights by center:
```{r}
ggplot(data, aes(x=weight)) + 
  geom_histogram(bins=50) + 
  facet_wrap( ~ production_center, ncol=1)
```

@@

## Ages

There seems to be an issue with some very negative values of age:
```{r}
range(data$age_in_days, na.rm=TRUE)
ggplot(data, aes(x=age_in_days)) + 
  geom_histogram(bins=50)
```

So for now we'll filter those out:

```{r}
data <- data %>% filter(age_in_days > 0 & age_in_days < 500)
```

Overall distribution of ages:
```{r}
ggplot(data, aes(x=age_in_days)) + 
  geom_histogram(bins=50)
```

Age by center:
```{r}
ggplot(data, aes(x=age_in_days)) + 
  geom_histogram(bins=50) + 
  facet_wrap( ~ production_center, ncol=1)
```

Age by center and sex:
```{r, fig_height=12}
ggplot(data, aes(x=age_in_days, fill=sex)) + 
  geom_histogram(bins=50) + 
  facet_wrap( ~ production_center, ncol=1)
```

Age vs weight by sex:
```{r}
ggplot(data, aes(x=age_in_days, y=weight)) + 
  geom_hex() + 
  viridis::scale_fill_viridis() + 
  coord_fixed() +
  facet_wrap( ~ sex, ncol=1)
```

## Procedures

@@

Note the uneven distribution of procdures by production_center. We can try to visualise the above (need to improve):
